Updates on the Exoplanet Orbit Database

### 2013-12-23 draft/ms.tex
Modify ms.tex to be in aastex preprint style, per PASP requirement.
Update ms.tex and new_table_items.txt. Outline paper structure in ms.tex.

\documentclass{emulateapj}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
\usepackage{graphicx}
\bibliographystyle{apj} 
\usepackage{epstopdf}  
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{verbatim}
\usepackage{morefloats} % somehow need this to have lots of figures
                        % and tables?
% for attractive links:
\usepackage[colorlinks,urlcolor=blue,citecolor=black,linkcolor=blue]{hyperref}
%\usepackage[nolists]{endfloat} % put floats at end - doesn't work
\interfootnotelinepenalty=10000 % Do not want cross-page footnote!

@@

\title{}

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ming Zhao\altaffilmark{1,2}}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN FIGURES AND STUFF
\begin{comment} % empty right now, so comment out
\newpage

%----------------------------------------------------------------
% Figure: 
\begin{figure*}[!th]
  \center
\includegraphics[angle=0.,scale=0.9]{f1.eps}  
\caption{
  \label{fig:f1}}
\end{figure*}
%----------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tables

%----------------------------------------------------------------
% Table: 
\renewcommand{\arraystretch}{1.3} % more row spacing for the table
\begin{turnpage}
\begin{center}
\begin{deluxetable*}{@{\hspace{-5mm}}c@{\hspace{-5mm}}llllccc}
%\rotate
\tabletypesize{\scriptsize}
\tablewidth{0pt}
\tablecaption{\label{tab:basic}}
\tablehead{
%-------------  
% FIRST ROW  
% submm stuff  
\colhead{} & \colhead{} &
\colhead{$S_{870 \mu{\rm m}}$} &
% xray stuff
\multicolumn{2}{c}{\xray\ Position\tablenotemark{b}}  & \colhead{\cdfs} & \colhead{\ecdfs} &
\colhead{$f_{X}/10^{-15}$} \\ \cline{4-5}
%-------------
% SECOND ROW
% submm stuff  
\colhead{ALESS SMG Full Name\tablenotemark{a}} & \colhead{ID\tablenotemark{a}} &
\colhead{(mJy)} &
% xray stuff
\colhead{$\alpha_{\rm J2000.0}$}  &  \colhead{$\delta_{\rm J2000.0}$}
& \colhead{Cat \& ID\tablenotemark{b}} & \colhead{Cat \& ID\tablenotemark{b}} &
\colhead{erg cm$^{-2}$ s$^{-1}$\tablenotemark{c}} 
}
\startdata
ALESS J$033213.85-275600.3  $ & 011.1 & $  7.3 \pm 0.4 $ & 03 32 13.85 & $ -27 $ 56 00.44 & M 197 & M 332 &  1.69 
\enddata
%
\tablenotetext{a}{}
%
\end{deluxetable*}
\end{center}
\end{turnpage}
%----------------------------------------------------------------

\end{comment}

>>>>

%\documentclass{emulateapj}
% Requirement of PASP to use preprint and aastex
\documentclass[12pt,preprint]{aastex}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
\usepackage{graphicx}
\bibliographystyle{apj} 
\usepackage{epstopdf}  
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{verbatim}
\usepackage{morefloats} % somehow need this to have lots of figures
                        % and tables?
% for attractive links:
\usepackage[colorlinks,urlcolor=blue,citecolor=black,linkcolor=blue]{hyperref}
%\usepackage[nolists]{endfloat} % put floats at end - doesn't work
\interfootnotelinepenalty=10000 % Do not want cross-page footnote!

@@

\title{Updates on the Exoplanet Orbit Database}

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ming Zhao\altaffilmark{1,2}}
\author{and Friends}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the EOD}\label{sec:update}

Restrict the updates in this section on EOD updates.

Parameter updates, new table parameters etc. What other updates are there?

Table: complete list of table parameters. Highlight the ones not
included in Wright\etal2011

Figure: Figure of single planet page, to show updated transit
parameters and RV curves etc.?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}

Figure: some comparison figures of Kepler candidate properties
vs. EOD planet properties, such as mass-period, mass-radius?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}\label{sec:conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments

@@
